---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# questionnaires: An R data package full of questionnaires

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/milanwiedemann/questionnaires.svg?branch=master)](https://travis-ci.com/milanwiedemann/questionnaires)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/milanwiedemann/questionnaires?branch=master&svg=true)](https://ci.appveyor.com/project/milanwiedemann/questionnaires)
<!-- badges: end -->

The goal is to provide a catalogue of questionnaire details (e.g item labels, response categories, references, and more) to speed up the reporting of results.

## Installation

You can install the development version from [GitHub](https://github.com/milanwiedemann/questionnaires) with:

``` r
# install.packages("devtools")
devtools::install_github("milanwiedemann/questionnaires")
```

## Examples

### Creating figures

```{r, fig.width = 7, fig.height = 5, dpi=200, out.width = "80%"}
# Load packages
library(ggplot2)
library(tibble)
library(questionnaires)
set.seed(1234)

# Create some data
df <- tibble(item = 1:7,
             score = sample(1:3, 7, replace = T))

# Create figure using short labels from gad7
ggplot(df, aes(x = factor(item), y = score, fill = factor(item))) +
  geom_bar(stat="identity") +
  ggplot2::scale_fill_viridis_d(labels = gad7$item_label_short) +
  labs(x = "Item", y = "Score", fill = gad7$measure)
```



```{r include=FALSE}
# First simulate some data ----
set.seed(123)
library(tidyverse)

# Simulate item by item data
sim_items <- function(n_items, n_ids, item_range, measure = "measure", item_weight = NULL, id_weight = NULL) {
    
  1:n_items %>%
        
  lapply(function(x) sample(item_range, 
                            n_ids, 
                            replace = TRUE,
                            prob = item_weight)) %>% 
        
    as.data.frame(col.names = paste0(measure, "_i", 1:n_items),
                  
                  row.names = paste0("id_", 1:n_ids))
}

sim_items(n_items = 4, n_ids = 3, measure = "gad7", item_range = 0:3)
    

seq_along(4)

```


### Creating Tables

This is a basic example which shows you how to create a table for the PHQ-9:

```{r phq9-table-example}
# Load packages ----
library(questionnaires) # For questionnaire data
library(dplyr) # For data manipulation
library(knitr) # For creating tables

phq9 %>%
    select(item_number, item_label_long) %>% 
    kable(col.names = c("Item", "Description"))

```

### Reference items in text 

Writing in RMardown it's easy to reference item labels in text using the following:

```{r, eval=FALSE}
Most clients showed most improvement on item 1 of the GAD-7 (*"`r questionnaires::gad7[[1, 4]]`"*)
```

Most clients showed most improvement on item 1 of the GAD-7 (*"`r questionnaires::gad7[[1, 4]]`"*)


## How to contribute / add more questionnaires

A new questionnaire can be added to this library by creating a dataset with all information in the [`create-measures.R`](data-raw/create-measures.R) in the `data-raw` folder of this repositoty.
Details for a new dataset needs to be added to [`data.R`](R/data.R) file in the data folder of this repositoty.

## TODO / TOTHINK

- Which licence would be appropriate for a data package like this?
- What are the legal challanges with copyright, license fees ... and does it even matter for a project like this?
- Which information about a measure should be available in the help files, e.g. internal consistentcy, test-retest reliability, cutoffs, ... ?
- How to best name data sets so it doesn't get confusing, e.g. `gad7` vs `general_health_anxiety_questionnaire_7item`?
- What's a good package name, e.g. `measureme`, `measureR`, `measuRes` vs `questionnaires`?
- What's the best data structure to store this information, especially when questionnaires are not straightforward, e.g. different repsonse categories for each item?
- How could different languages of the same questionnaire be integrated, e.g. suffix `_en` for English, `_de` for German?
